### 2020-03-14 2020.csic5011/homework/homework04.tex
Add files via upload

\lecture{Homework 2. Random Projections}{Yuan Yao}{Due: Open Date}{Sep. 15, 2017}

@@

\url{https://www.dropbox.com/l/scl/AADN80paNFy1yB5gyYzNVOfkZGj9SiVDlZo}

@@

>>>>

\lecture{Homework 4. Random Projections}{Yuan Yao}{Due: in 1.5 weeks}{Mar. 11, 2020}

@@

\url{https://drive.google.com/file/d/1KMLPEG91mnzdK2pUlq2BkjOx2BsaZy9s/view?usp=sharing}

@@

Another cleaned dataset is due to Quanhua MU and Yoonhee Nam:

\begin{itemize}
\item Genotyped data of the 1043 ($n$) subjects. 0(AA), 1(AC), 2(CC). Missing values are removed, only autosomal SNPs were selected ($p\approx 400K$). Google drive link: \\
\url{https://drive.google.com/file/d/1a9I8_akfCMHBRrPMdnWkjyL9fKcQbJJq/view?usp=sharing}
\item Sample Information of 1043 subjects. Google drive link: \\
\url{https://drive.google.com/file/d/11Q-8B57WDQnrIV92b-h_WLqDGviiYsm2/view?usp=sharing} \\
\end{itemize}
